\section*{Acknowledgements and Disclaimer}
Work for the \textbf{remoter} package is supported in part by the project 
*Harnessing Scalable Libraries for Statistical Computing on Modern Architectures 
and Bringing Statistics to Large Scale Computing* funded by the National 
Science Foundation Division of Mathematical Sciences under Grant No. 1418195.

Any opinions, findings, and conclusions or recommendations expressed in  this 
material are those of the authors and do not necessarily reflect the  views of 
the National Science Foundation.  The findings and conclusions in this article 
have not been formally disseminated by the U.S. Department of Health \& Human 
Services nor by the U.S. Department of Energy, and should not be construed to 
represent any determination or policy of University, Agency, Administration and 
National Laboratory.

The \textbf{remoter} logo comes from the image
``\href{https://commons.wikimedia.org/wiki/File:Tr\%C3\%A5dtelefon-illustration.png\#/media/File:Tr\%C3\%A5dtelefon-illustration.png}{Tradtelefon-illustration}''. 
Licensed under Public Domain via Commons.

This manual may be incorrect or out-of-date.  The author(s) assume
no responsibility for errors or omissions, or for damages resulting
from the use of the information contained herein.

This publication was typeset using \LaTeX.

\vfill

\null
\vfill
\copyright\ 2015--2016 Drew Schmidt.

Permission is granted to make and distribute verbatim copies of
this vignette and its source provided the copyright notice and
this permission notice are preserved on all copies.
